BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2017-03-29 Paper2/BOAST.tex
Better explain vectorization. Answers to point 2) of reviewer.

\paragraph{Vectorization} The first proposed optimization involves computing
five pixels instead of one using the vectors available on the Mali
architecture. The vectors have to be kept in memory to ensure an efficient
execution. Using vectors of 16 elements, 15 useful components are
simultaneously loaded and can be used in computation.  This optimization yields
speedups between 1.5 and 6 depending on the image size.

@@

  int16 res = v22 * (int)9 - v11 - v12 - v13 - v21 - v23 - v31 - v32 - v33;
        res = clamp(res, (int16)0, (int16)255);
  uchar res_ = convert_uchar16(res);

  vstore8(res_.s01234567, 0, dst + 3*width*j + 3*5*i);
  vstore8(res_.s89ab,     0, dst + 3*width*j + 3*5*i + 8);
  vstore8(res_.scd,       0, dst + 3*width*j + 3*5*i + 12);
  dst[3*width*j + 3*5*i + 14] = res_.se;
}
\end{lstlisting}

>>>>

\paragraph{Vectorization} The first proposed optimization involves computing
five pixels instead of one using the vectors available on the Mali
architecture. This is done using the native OpenCL support for vectorization.
For instance \emph{vload16} load 16 consecutive elements from memory and stores
it a vector.  Here the loaded vector is of type \emph{uchar16} meaning that it
is a vector of 16 consecutive bytes. In order to do computations without
overflowing, those vectors have to be converted (using \emph{convert\_int16}) to
a signed and bigger integer type.  Here they are converted to signed 4 bytes
integers, leading to a vector size of 64 bytes.

Once those vector are loaded they can be used in Single Instruction Multiple
Data (SIMD) paradigm. Operations are done component-wise on the vector. For
instance, \emph{v22 * (int16)9} multiplies each component of the vector by 9.
The same thing goes for the difference operator. Once computed, the result is
clamped and converted back to bytes using \emph{convert\_uchar16}.

Using vectors of 16 elements, 5 pixels (15 components) can be simultaneously
loaded and can be used in computation. Here the developer chose a pixel based
approach and thus decided to only save the 15 relevant components. These
components are saved in a vector manner using the power of two decomposition
of 15. The first 8 components (0-7) are saved using \emph{vstore8} then the
next 4 (8,9,a,b) using \emph{vstore4} and so on.

This optimization yields speedups between 1.5 and 6 depending on the image size.

@@

  int16 res = v22 * (int16)9 - v11 - v12 - v13 - v21 - v23 - v31 - v32 - v33;
        res = clamp(res, (int16)0, (int16)255);
  uchar res_ = convert_uchar16(res);

  vstore8(res_.s01234567, 0, dst + 3*width*j + 3*5*i);
  vstore4(res_.s89ab,     0, dst + 3*width*j + 3*5*i + 8);
  vstore2(res_.scd,       0, dst + 3*width*j + 3*5*i + 12);
  dst[3*width*j + 3*5*i + 14] = res_.se;
}
\end{lstlisting}
